ETH-Paid Internet Access\\ {\smaller \textbf{Proyecto final de m\'aster (versi\'on texto en Espa\~nol)}}

### 2019-09-30 Paper.tex

\input{Version.tex}
% Default rendering options
\definecolor{pagecolor}{rgb}{1,0.98,0.9}
\def\YellowPaperVersionNumber{unknown revision}
\IfFileExists{Options.tex}{\input{Options.tex}}

@@

\setlength{\columnsep}{20pt}
\begin{multicols}{2}

\section{Introducci\'on}\label{sec:introduction}

@@

  \includegraphics[keepaspectratio, width=0.2\textwidth]{images/lafonera-sourcewikipedia}

@@

  \includegraphics[keepaspectratio, width=0.2\textwidth]{images/rpi3modelb-sourceamazon.png}

@@

  \includegraphics[keepaspectratio, width=0.481125\textwidth]{images/ethcurrentprice-sourcecoinbase}

@@

  \includegraphics[keepaspectratio, width=0.481125\textwidth]{images/swarm-diagram-sourcedocker}

>>>>

% \input{Version.tex}
% Default rendering options
\definecolor{pagecolor}{rgb}{1,0.98,0.9}
\def\YellowPaperVersionNumber{unknown revision}
\IfFileExists{Options.tex}{\input{Options.tex}}

@@

\tableofcontents

\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\section{Introducci\'on}\label{sec:introduction}

@@

  \includegraphics[keepaspectratio, width=0.2\textwidth]{images/lafonera-sourcewikipedia.eps}

@@

  \includegraphics[keepaspectratio, width=0.2\textwidth]{images/rpi3modelb-sourceamazon.eps}

@@

  \includegraphics[keepaspectratio, width=0.481125\textwidth]{images/ethcurrentprice-sourcecoinbase.eps}

@@

  \includegraphics[keepaspectratio, width=0.481125\textwidth]{images/swarm-diagram-sourcedocker.eps}
